---
title: "MSD 54-Plex Analysis and APLCO Calprotectin Analysis"
author: "Kang Dong | Centre for Heart Lung Innovation, University of British Columbia"
date: "October 3, 2021"
output:
  pdf_document:
    toc: yes
    number_sections: yes
---

```{r, echo=FALSE}
# Input Data
library(readxl)

# Data manipulation
library(tidyverse)

# Data visualization
library(ggplot2)
library(ggpubr)
library(ggsci)
library(ggfortify)
library(ggrepel)

# Statistical analysis
library(edgeR)
library(limma)
library(psych)

# Machine learning
library(caret)
library(tidymodels)
library(pROC)

# Report generation
#library(knitr)

# Results path
resultsPath <- "Final_results/MSD"
```

# R function

## Pre-process MSD data: "preprocessMSD(filePath, dataSheet, standardSheet, sampleInfo)"
```{r}
preprocessMSD <- function(filePath, dataSheet, standardSheet, sampleInfo) {
  # Step 1. Create Empty List
  output <- list()
  
  # Step 2. Extract Study Data
data <- read_excel(path = filePath, sheet = dataSheet) %>%
  as.data.frame() %>%
  mutate(UniqueID = paste(Plate, Sample, sep = "-")) %>%
  filter(UniqueID %in% sampleInfo$UniqueID)

# Step 3. Extract Standard
standard <- read_excel(path = filePath, sheet = standardSheet) %>%
  dplyr::select(Plate, Assay, Spot, `Detection Limits: Calc. Low`, `Detection Limits: Calc. High`)

# Step 4. Add Standard and sampleInfo to Data
data <- left_join(data, standard, by = c("Plate", "Assay", "Spot"))
data <- left_join(data, sampleInfo, by = c("Plate", "Sample", "UniqueID"))

data <- data %>% dplyr::select(SampleID, SubjectID, Plate, Sample, UniqueID, Assay, `Calc. Concentration`, `Calc. Conc. Mean`, `Calc. Conc. CV`, `Detection Limits: Calc. Low`, `Detection Limits: Calc. High` )

# Step 5. Save `data` to `output` list
output$data <- data

# Step 6. Summarize sample below low detection limits an CV
summaryTable <- data %>% 
  mutate(above_low = ifelse(`Calc. Conc. Mean` > `Detection Limits: Calc. Low`, TRUE, FALSE)) %>%
  #dplyr::select(Plate, Sample, Assay, `Calc. Conc. Mean`, `Calc. Conc. CV`, UniqueID, `Detection Limits: Calc. Low`, SubjectID, above_low) %>%
  dplyr::select(-`Calc. Concentration`) %>%
  distinct() %>%
  group_by(Assay) %>%
  summarise(undetected = sum(above_low == FALSE | is.na(above_low)),
            `CV ≤ 5%` = sum(`Calc. Conc. CV` <= 5, na.rm = TRUE),
            `5% < CV ≤ 10%` = sum(`Calc. Conc. CV` > 5 & `Calc. Conc. CV` <= 10, na.rm = TRUE),
             `10% < CV ≤ 15%` = sum(`Calc. Conc. CV` > 10 & `Calc. Conc. CV` <= 15, na.rm = TRUE),
             `15% < CV ≤ 20%` = sum(`Calc. Conc. CV` > 15 & `Calc. Conc. CV` <= 20, na.rm = TRUE),
             `25% < CV ≤ 30%` = sum(`Calc. Conc. CV` > 25 & `Calc. Conc. CV` <= 30, na.rm = TRUE),
             `30% < CV ≤ 35%` = sum(`Calc. Conc. CV` > 30 & `Calc. Conc. CV` <= 35, na.rm = TRUE),
            `CV > 35%` = sum(`Calc. Conc. CV` > 35, na.rm = TRUE),
            CV_NA = sum(is.na(`Calc. Conc. CV`))) %>%
  mutate(undetected_pct = round(undetected/nrow(sampleInfo), digits = 2))

# Step 7. Save `summaryTable` to `output` list
output$summaryTab <- summaryTable

return(output)
}
```

## Plot CV vs. Protein levels (pg/mL)
```{r}
plotCV <- function(data) {
 p <- ggplot(data, aes(x = `Calc. Conc. CV`, y = `Calc. Concentration`)) +
    geom_point() +
    facet_wrap(Assay ~ Plate, ncol = 5, scale = "free_y") +
    geom_hline(aes(yintercept = `Detection Limits: Calc. Low`), color = "dodgerblue3", linetype = 2, size = 0.75) +
    geom_vline(xintercept = c(15, 35), color = "firebrick1", linetype = 2, size = 0.75) +
    scale_x_continuous(breaks = c(seq(0, 100, by = 10))) +
    labs(title = "CV vs. Calculate Concentration", x = "Coefficient of variation (CV)", y = "Calculate Concentration, pg/mL" ) +
    theme_bw()
  return(p)
    }
```

# Pre-process Data : MSD

## Sample grouping variables
```{r}
sampleInfo <- read_excel(path = "MSD/MSD 54plex Data.xlsx", sheet = "Sample ID") %>% 
  as.data.frame() %>%
  mutate(SampleID = substring(SampleID, 0, nchar(SampleID) - 4)) %>%
  mutate(SubjectID = substring(SampleID, 0, 6),
         UniqueID = paste(Plate, Sample, sep = "-"))

# Keep CFTR Study
sampleInfo <- filter(sampleInfo, Study == "CFBiomarker")
```

## Proinflammatory Panel

```{r}
proinflammatoryData <- preprocessMSD(filePath = "MSD/MSD 54plex Data.xlsx", dataSheet = "Proinflammatory Panel", standardSheet = "Proinflammatory Panel-Standard", sampleInfo)
proinflammatoryData$summaryTab
```

```{r}
p <- plotCV(proinflammatoryData$data)
#ggsave(filename = paste(resultsPath, "CV-Proinflammatory.png", sep = "/"), p, width = 16, height = 8)
```

## Cytokine Panel 1

```{r}
cytokine1Data <- preprocessMSD(filePath = "MSD/MSD 54plex Data.xlsx", dataSheet = "Cytokine Panel 1", standardSheet = "Cytokine Panel 1-Standard", sampleInfo)
cytokine1Data$summaryTab
```

```{r}
p <- plotCV(cytokine1Data$data)
#ggsave(filename = paste(resultsPath, "CV-Cytokine 1.png", sep = "/"), p, width = 16, height = 8)
```

## Cytokine Panel 2

```{r}
cytokine2Data <- preprocessMSD(filePath = "MSD/MSD 54plex Data.xlsx", dataSheet = "Cytokine Panel 2", standardSheet = "Cytokine Panel 2-Standard", sampleInfo)
cytokine2Data$summaryTab
```

```{r}
p <- plotCV(cytokine2Data$data)
#ggsave(filename = paste(resultsPath, "CV-Cytokine 2.png", sep = "/"), p, width = 16, height = 8)
```

## Chemokine Panel 1

```{r}
chemokine1Data <- preprocessMSD(filePath = "MSD/MSD 54plex Data.xlsx", dataSheet = "Chemokine Panel 1", standardSheet = "Chemokine Panel 1-Standard", sampleInfo)
chemokine1Data$summaryTab
```

```{r}
p <- plotCV(chemokine1Data$data)
#ggsave(filename = paste(resultsPath, "CV-Chemokine 1.png", sep = "/"), p, width = 16, height = 8)
```

## TH17 Panel

```{r}
th17Data <- preprocessMSD(filePath = "MSD/MSD 54plex Data.xlsx", dataSheet = "Th17 Panel", standardSheet = "Th17 Panel-Standard", sampleInfo)
th17Data$summaryTab
```

```{r}
p <- plotCV(th17Data$data)
#ggsave(filename = paste(resultsPath, "CV-Th17.png", sep = "/"), p, width = 16, height = 8)
```

## Vascular Injury Panel
```{r}
vascularData <- preprocessMSD(filePath = "MSD/MSD 54plex Data.xlsx", dataSheet = "Vascular Injury Panel", standardSheet = "Vascular Injury Panel-Standard", sampleInfo)
```

## Angiogenesis Panel 1

```{r}
angiogenesisData <- preprocessMSD(filePath = "MSD/MSD 54plex Data.xlsx", dataSheet = "Angiogenesis Panel 1", standardSheet = "Angiogenesis Panel 1-Standard", sampleInfo)
```

## Summary table and data
```{r}
# Summary Table
summaryTab_MSD <- rbind(proinflammatoryData$summaryTab, cytokine1Data$summaryTab, cytokine2Data$summaryTab, chemokine1Data$summaryTab, th17Data$summaryTab, vascularData$summaryTab, angiogenesisData$summaryTab)

# Data Table
dataTab_MSD <- rbind(proinflammatoryData$data, cytokine1Data$data, cytokine2Data$data, chemokine1Data$data, th17Data$data, vascularData$data, angiogenesisData$data) %>%
  dplyr::select(-`Calc. Concentration`) %>%
  distinct()
```

## Inclusion criteria for analytes
```{r}
# QC on PEx samples
drop_assay <- filter(summaryTab_MSD, undetected_pct >= 0.25 | Assay == "hsIL-8")$Assay
dataTab <- dataTab_MSD[which(dataTab_MSD$Assay %in% drop_assay),]

load(file = "biomarkerData/biomarkerData.RData")
PEx <- filter(pDataPEx, type == "PEx")

plotdata <- dataTab[which(dataTab$SampleID %in% PEx$sampleID),] %>%
  mutate(below_detect = ifelse(`Calc. Conc. Mean` < `Detection Limits: Calc. Low` | is.na(`Calc. Conc. Mean`), TRUE, FALSE))

table(plotdata$Assay, plotdata$below_detect)
```

IL-17A Gen.B, IL-17A/F, IL-17B, IL-3 are detectable in stable vs. PEx samples.

```{r}
# Kept and droped Assays
keep_assay <- filter(summaryTab_MSD, !undetected_pct >= 0.25 & !Assay == "hsIL-8")$Assay
keep_assay <- c(keep_assay, "IL-17A Gen.B", "IL-17A/F", "IL-17B", "IL-3")
keep_assay
```

In total, 51 analytes are detectable in plasma.

```{r}
# Update the dataTab with `keep_assay`
dataTab_MSD <- dataTab_MSD[which(dataTab_MSD$Assay %in% keep_assay),]
```

## Data manipulation based on QC
```{r}
# For value is NA or below lower detection limits, replace them with half of the lower detection limits
dataTab_MSD <- dataTab_MSD %>% mutate(below_detect = ifelse(`Calc. Conc. Mean` < `Detection Limits: Calc. Low` | is.na(`Calc. Conc. Mean`), TRUE, FALSE))

dataTab_MSD[which(dataTab_MSD$below_detect == TRUE),]$`Calc. Conc. Mean` <- 0.5 * dataTab_MSD[which(dataTab_MSD$below_detect == TRUE),]$`Detection Limits: Calc. Low`

dataTab_MSD <- dplyr::select(dataTab_MSD, -below_detect)
```


# Pre-process Data: Calprotectin (Convert ng/mL to pg/mL)
```{r}
CALP <- read_excel(path = "MSD/APLCO-Calprotectin Data.xlsx", sheet = "Calprotectin Data")

CALP <- CALP %>% mutate(SampleID = substr(SampleID, 0, nchar(SampleID) - 4))
CALP <- CALP[which(CALP$SampleID %in% sampleInfo$SampleID),]
CALP <- CALP %>% mutate(`Value_pg/ml` = 1000 * AdjResult)
```

```{r}
preprocessData_MSD <- list(summaryTable = summaryTab_MSD, MSD = dataTab_MSD, Calprotectin = CALP)
#save(preprocessData_MSD, file = paste(resultsPath, "preprocesseData_MSD.RData", sep = "/"))
```


# Exploratory data analysis

```{r}
load(paste(resultsPath, "preprocesseData_MSD.RData", sep = "/"))
load(file = "biomarkerData/biomarkerData.RData")
```

```{r}
msd <- preprocessData_MSD$MSD %>%
  dplyr::select(SampleID, Assay, `Calc. Conc. Mean`) %>%
  dplyr::rename(value = `Calc. Conc. Mean`)

calp <- preprocessData_MSD$Calprotectin %>%
  mutate(Assay = rep("Calprotectin", times = nrow(preprocessData_MSD$Calprotectin))) %>%
  dplyr::select(SampleID, Assay, `Value_pg/ml`) %>%
  dplyr::rename(value = `Value_pg/ml`)

dataTab <- rbind(msd, calp)
```

```{r}
p <- dataTab %>%
  ggplot(aes(x = reorder(Assay, value, FUN = median), y = value)) +
  geom_boxplot() +
  theme_bw() +
  scale_y_continuous(trans = "log10") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, face = "bold"),
        axis.text.y = element_text(face = "bold"),
        axis.title.y = element_text(face = "bold")) +
  labs(x = "", y = "Concentration, pg/mL")

#ggsave(filename = paste(resultsPath, "Concentration-boxplot.png", sep = "/"), p, width = 16, height = 6)
```


```{r}
# Distribution of Raw Data
p <- ggplot(dataTab, aes(value)) +
  geom_histogram() +
  facet_wrap(~Assay, scales = "free", ncol = 8 ) +
  labs(x = "Concentration", y = "Count") +
  theme_bw()

# Distribution of Log2 transformed Data
p <- ggplot(dataTab, aes(log2(value))) +
  geom_histogram() +
  facet_wrap(~Assay, scales = "free", ncol = 8 ) +
  labs(x = "Concentration", y = "Count") +
  theme_bw()
#ggsave(filename = paste(resultsPath, "Histogram Data.png", sep = "/"), p, width = 16, height = 10)
```

# PCA

```{r}
library(mixOmics)
library(corrplot)
library(RColorBrewer)

# Prepare data
clinical <- pDataPEx %>% column_to_rownames(var = "sampleID")
count <- dataTab %>% pivot_wider(names_from = Assay, values_from = value) %>% 
  column_to_rownames(var = "SampleID") %>% log2()

count <- count[rownames(clinical), ]
all(rownames(clinical) == rownames(count))

# PCA
results.pca <- mixOmics::pca(count, ncomp = 5, center = TRUE, scale = FALSE)

p <- plotIndiv(results.pca, comp = c(1,2),
          ind.names = FALSE,
          #group = clinical$type, 
          group = clinical$sex, 
          title = "Stable vs. PEx",
          legend = TRUE, legend.title = ""
          )

#ggsave(filename = paste(resultsPath, "PCA-Stable vs PEx-Sex-PC2-3.png", sep = "/"), p$graph, width = 6, height = 4)

# PCs vs. Clinical Variables
PC <- results.pca$variates$X %>% as.data.frame()
all(rownames(PC) == rownames(clinical)) 

plotdata <- cbind(PC, clinical) %>%
  dplyr::select(contains("PC"), Age, sex, BMI, ppFEV1, CRISS, contains("differential")) %>%
  mutate(Sex = case_when(sex == "M" ~ 1, sex == "F" ~ 0)) %>%
  # Rename "cell differential" to "cell %"
  dplyr::rename(`Neutrophil (%)` = Neutrophil_differential, `Lymphocyte (%)` =  Lymphocyte_differential, `Monocyte (%)` = Monocyte_differential, `Eosinophil (%)` = Eosinophil_differential, `Basophil (%)` = Basophil_differential) %>%
  dplyr::select(-sex) %>%
  # Re-order the variable
  dplyr::select(contains("PC"), contains("(%)"), Age, Sex, BMI, ppFEV1, CRISS)


keepCol <- names(dplyr::select(plotdata, contains("PC")))
keepRow <- names(dplyr::select(plotdata, -contains("PC")))

corr <- round(cor(plotdata, use = "complete.obs", method = "spearman"), 2)
corr <- corr[keepRow, keepCol]

testRes = cor.mtest(plotdata, use = "complete.obs", method = "spearman", conf.level = 0.95)
p.mat <- testRes$p[keepRow, keepCol]

pdf(file = paste(resultsPath, "PCA-Stable vs PEx-PCs.pdf", sep = "/"))
corrplot(corr, p.mat = p.mat, sig.level = 0.05, insig = "label_sig", pch.cex = 1.5, method = "circle", tl.cex = 0.75, cl.pos = 'b', cl.cex = 0.5, col = rev(brewer.pal(n = 8, name = "RdBu")))
dev.off()


results.pca$loadings
```


# Differential expression analysis

## Stable vs. PEx
```{r}
count <- dataTab %>% pivot_wider(names_from = Assay, values_from = value) %>% 
  column_to_rownames(var = "SampleID") %>% log2()
exp <- count[pDataPEx$sampleID,] %>% t()
all(colnames(exp) == pDataPEx$sampleID)

design <- model.matrix(~0 + type, data = pDataPEx)
cor <- duplicateCorrelation(exp, design, block = pDataPEx$subject)

fit <- lmFit(exp, design, block = pDataPEx$subject, correlation = cor$consensus)
contrast <- makeContrasts(comp = typePEx - typestable, levels = design)
fit <- contrasts.fit(fit, contrast)
fit <- eBayes(fit)

results.DE.MSD <- topTable(fit, n = Inf, coef = "comp", sort.by = "p", adjust.method="BH") %>%
  rownames_to_column(var = "Assay")

#write.csv(results.DE.MSD, file = paste(resultsPath, "DE_MSD.csv", sep = "/"), row.names = FALSE)
```

```{r}
# Volcano Plot
p <- results.DE.MSD %>%
  mutate(sig = case_when(`adj.P.Val` < 0.1 ~ "FDR < 0.1",
                         `adj.P.Val` >= 0.1 ~ "FDR ≥ 0.1")) %>%
  ggplot(aes(x = logFC, y = -log10(P.Value))) +
  geom_point(aes(color = sig), size = 1.5) +
  scale_color_manual(values = c("firebrick4", "dodgerblue4")) +
   # Fold change
  annotate(geom = "vline", xintercept = c(-log2(1.5), log2(1.5)), x = c(-log2(1.5), log2(1.5)), linetype = c("dashed", "dashed")) +
  annotate(geom = "text", label = c("FC < -1.5", "FC > 1.5"), x = c(-log2(1.5), log2(1.5)), y = c(0, 0), angle = 0, hjust = c(1.25, -0.25)) +
  # p-value = 0.05 and FDR = 0.1 (p value = 0.007985579)
  annotate(geom = "hline", yintercept = -log10(0.05), y = -log10(0.05) , linetype = "dashed") +
  annotate(geom = "text", label = "p-value < 0.05", y = -log10(0.05), x = -1.25, angle = 0, vjust = -1) +
  # Add gene name
  geom_text_repel(data = filter(results.DE.MSD, P.Value < 0.05 | abs(logFC) > log2(1.5)), aes(label = Assay) ,size = 2.5, max.overlaps = Inf) +
  # Chance label on x and y axis
  labs(x = ~Log[2]~ 'fold change', y = ~-Log[10]~italic(P-value), color = "") +
  # Set theme
  xlim(-1.5,1.5) +
  theme_pubr()
p
ggsave(filename = paste(resultsPath, "Volcanoplot_MSD.png", sep = "/"), p, dpi = 320, height = 4, width = 6)
```


## Visulize single markers
```{r}
clinical <- pDataPEx %>% dplyr::rename(SampleID = sampleID)
# Calprotectin, SAA, and CRP
p1 <- dataTab %>% 
  inner_join(., clinical, by = "SampleID") %>%
  mutate(type = factor(type, levels = c("stable", "PEx"))) %>%
  filter(Assay == "Calprotectin" | Assay == "SAA" | Assay == "CRP") %>%
  mutate(value = value * 1e-06,
         Assay = factor(Assay, levels = c("CRP", "SAA", "Calprotectin"))) %>%
  ggplot(aes(x = type, y = value, fill = type)) +
  geom_boxplot() +
  geom_line(aes(group = subject), color = "dimgrey") +
  geom_point() +
  facet_wrap(~Assay, scales = "free_y") +
  scale_fill_lancet() +
  labs(x = "", y = "Concentration, mg/L", fill = "") +
  theme_pubr()

# PIGF
p2 <- dataTab %>% 
  inner_join(., clinical, by = "SampleID") %>%
  mutate(type = factor(type, levels = c("stable", "PEx"))) %>%
  filter(Assay == "PIGF") %>%
  ggplot(aes(x = type, y = value, fill = type)) +
  geom_boxplot() +
  geom_line(aes(group = subject), color = "dimgrey") +
  geom_point() +
  facet_wrap(~Assay, scales = "free_y") +
  scale_fill_lancet() +
  labs(x = "", y = "Concentration, pg/mL", fill = "") +
  theme_pubr() +
  scale_y_continuous(trans = "log10")

#ggsave(filename = paste(resultsPath, "DE Markers.IL17A IL-17C.png", sep = "/"), p5, dpi = 320, height = 3, width = 4)
```

# Use Calprotectin to predict imminent PEx
```{r}
clinical <- pDataImminent %>% dplyr::rename(SampleID = sampleID)

data <- dataTab %>% 
  left_join(clinical,. , by = "SampleID") %>%
  mutate(Y = ifelse(type == "stable", "s", "p")) %>%
  mutate(Y = factor(Y, levels = c("s", "p"))) %>%
  filter(Assay == "Calprotectin") %>%
  mutate(value.log2 = log2(value))
```

```{r}
# Split training and testing data 75% vs. 25%
set.seed(666)
trainIndex <- createDataPartition(data$type, p = 0.75, list = FALSE, times = 5)
trainIndex

# Resample 4 were selected
trainData <- data[trainIndex[,4],]
testData <- data[-trainIndex[,4],]

# Training Model
## Features and Response Variables
X <- trainData$value
Y <- trainData$Y

## Train Control
folds <- groupKFold(trainData$subject, k = length(unique(trainData$subject)))

trainctrl <- trainControl(index = folds, method = "cv", summaryFunction = twoClassSummary, classProbs = TRUE, verboseIter = FALSE, savePredictions = TRUE)

## Fit Model
set.seed(666)
model.CALP  <- train(Y ~ value.log2, trainData, method = "glm", metric = "ROC", trControl = trainctrl, preProcess = c('center', 'scale'))

getTrainPerf(model.CALP)

# Testing Model
pred <- predict(model.CALP, testData, type = "prob")
roc.CALP <- roc(testData$Y, pred$p, uc = TRUE, plot = TRUE)
auc(roc.CALP)
```

```{r}
# auROC plot 
p <- ggroc(list(`Calprotectin (AUC = 0.75)`= roc.CALP), legacy.axes = TRUE, alpha = 0.75, size = 1) +
  geom_segment(aes(x = 0, xend = 1, y = 0, yend = 1), color="grey", linetype="dashed") +
  labs(color = "") +
  theme_pubr(legend = "bottom") + 
  scale_color_lancet()

#ggsave(filename = paste(resultsPath, "AUC.CALP.png", sep = "/"), p, dpi = 320, height = 3, width = 4)
#save(trainData, testData, model.CALP, file = paste(resultsPath, "Model.CALP.RData", sep = "/"))
```


# Use DE protein (p-value < 0.05) to predict imminent PEx

```{r}
sig.Protein <- filter(results.DE.MSD, P.Value < 0.05)

clinical <- pDataImminent %>% dplyr::rename(SampleID = sampleID)

data <- dataTab %>%
  mutate(value = log2(value)) %>% # log2 transfer the value 
  pivot_wider(names_from = Assay, values_from = value) %>%
  dplyr::select(SampleID, sig.Protein$Assay) %>%
  left_join(clinical,. , by = "SampleID") %>%
  mutate(Y = ifelse(type == "stable", "s", "p")) %>%
  mutate(Y = factor(Y, levels = c("s", "p")))
```

```{r}
# Resample 4 were selected
trainData.2 <- data[trainIndex[,4],]
testData.2 <- data[-trainIndex[,4],]

all(trainData.2$SampleID == trainData$SampleID)
all(testData.2$SampleID == testData$SampleID)
```

```{r}
## Features and Response Variables
X <- trainData.2 %>% dplyr::select(sig.Protein$Assay)
Y <- trainData.2$Y

## Fit Model
set.seed(666)
model.MSD  <- train(X, Y, method = "rf", tuneLength = 1000, metric = "ROC", trControl = trainctrl, importance = TRUE, na.action = na.pass, preProcess = c('center', 'scale'))
varImp(model.MSD)

getTrainPerf(model.MSD)

# Testing Model
pred <- predict(model.MSD, testData.2, type = "prob")
roc.MSD <- roc(testData.2$Y, pred$p, uc = TRUE, plot = TRUE)
auc(roc.MSD)
```

```{r}
# auROC plot 
p <- ggroc(list(`Inflammatory markers (AUC = 0.63)`= roc.MSD), legacy.axes = TRUE, alpha = 0.75, size = 1) +
  geom_segment(aes(x = 0, xend = 1, y = 0, yend = 1), color="grey", linetype="dashed") +
  labs(color = "") +
  theme_pubr(legend = "bottom") + 
  scale_color_lancet()

ggsave(filename = paste(resultsPath, "AUC.MSD.png", sep = "/"), p, dpi = 320, height = 3, width = 4)
#save(trainData, testData, model.CALP, file = paste(resultsPath, "Model.CALP.RData", sep = "/"))
```
